---
title: "Schedule"
---

```{r include = FALSE}
library(dplyr)
library(stringr)
library(readr)
library(tidyr)

lec.root = "https://raw.githubusercontent.com/stats-432sp2018/lectures/master/"

rawdat <- read.csv("schedule.csv")
cdat <- rawdat %>%
  mutate(ugly_date = ISOdate(2018, match(month, month.name), day),
         date = sprintf("%s-%02d %s",
                        tolower(months(ugly_date, abbreviate = TRUE)),
                        day, tolower(weekdays(ugly_date,abbreviate = TRUE))),
         topic = topic,
         action = action)


## Deal with linking notes when desired
cdat$notes_name = paste0(cdat$notes,'.pdf')
cdat$notes_name[cdat$notes_name=='.pdf'] = ' '
cdat$full_path = paste0(lec.root, cdat$notes_name)
cdat$notes1 = rep('(pdf)',nrow(cdat))
cdat$notes1 = str_replace(cdat$notes1, "(pdf)", '<a href="LINK">\\1</a>')
exist_pdfs = list.files("../lectures/", 'pdf')
link_them = cdat$link_it & (cdat$notes_name %in% exist_pdfs)
cdat$notes1[!link_them] = ' '
cdat <- cdat %>% mutate(notes = str_replace(notes1, '\"LINK\"', full_path))
rownames(cdat) <- NULL

## Link all reading responses
nrrs = 14
exist_dirs = list.dirs("../", recursive = FALSE, full.names = FALSE)
exist_rrs = exist_dirs[grepl('rr', exist_dirs)]
rrlinks = paste0('https://github.com/stats-432sp2018/', exist_rrs)
allrrs = paste0('rr',1:nrrs)
cdat$rr = character(nrow(cdat))
rrlinks = c('https://github.com/stats-432sp2018/class-roster', rrlinks)
allrrs[1:length(rrlinks)] = paste0('<a href=',
                                   rrlinks,'>',allrrs[1:length(rrlinks)],'</a>')
cdat$rr[seq(2,2*nrrs,by=2)] = allrrs
cdat$rr[!grepl('http',cdat$rr)] = ''
```


* Schedule is subject to change. See the [lectures repo](https://github.com/stats-432sp2018/lectures) for all materials. It is possible that more notes are in that repo but not linked here. _If you are looking for notes, check there before messaging me._  

* Actions in parentheses `(some action)` indicate optional/supplemental readings.

AEPV = [_Advanced Data Analysis from an Elementary Point of View_](http://www.stat.cmu.edu/~cshalizi/ADAfaEPoV/ADAfaEPoV.pdf)  
ISL = [_Introduction to Statistical Learning_](http://www-bcf.usc.edu/~gareth/ISL/)  
HGR = [_Happy Git with R_](http://happygitwithr.com/)  
R4DS = [_R for Data Science_](http://r4ds.had.co.nz)  
PC = Project Checkpoint

```{r results = 'asis', echo = FALSE}
options(knitr.kable.NA=' ')
knitr::kable(cdat %>% select(date, topic, notes, reading, action, rr))
```